Search for Spatially Extended Fermi-LAT Sources Using Two Years of Flight Data

### 2011-08-08 extended_catalog/paper/extended_catalog.tex
work on the conclusion

In \pointlike, it is assumed that the spatial and spectral model
of an extended source decouple and that the spatial shape can be
represented by a two dimensional function.  To fit the extended source,
\pointlike convolves the extended source shape with the PSF (as a
function of energy) and uses the \minuit fitting library to maximize
the likelihood by simultaneously fitting the position and extension
of the source (\cite{minuit_documentation}).  As will be described in
section~\ref{monte_carlo_validation}, simultaneously fitting the position
and extension is necessary to correctly calculate the statistical
significance of the detection of extension.  For each position and
extension, the spectral parameters of the sky model are refit. To avoid
projection effects, what is directly fit is not the longitude and latitude
but instead the source's displacement in a rotated reference frame.

The significance of the extension of a source can be calculated from
\tsext, which is defined as twice the increase in log likelihood (\loglikelihood)
between
the extended source model at its best fit values and the point source
model at its best fit values:
\begin{equation}
  \tsext=2\log(\loglikelihood_\text{ext}/\loglikelihood_\text{ps}).
\end{equation}
\pointlike calculates \tsext by fitting a source first with a spatially
extended model and then as a point source.  The interpretation
of \tsext in terms of a statistical significance is discussed in
section~\ref{monte_carlo_validation}.

The convolution of radially symmetric extended sources is optimized by
using a semi-analytic calculation.  The observed photon distribution
can be written as the convolution of the source shape ($I_\text{src}$)
with the PSF
\begin{equation}
  \text{PDF}(\vec r) = \int  \text{PSF}(|\vec r - \vec r'|)I_\text{src}(\vec r') d A'.
\end{equation}
For the LAT, the PSF is parameterized by a {\em King function}
\begin{equation}
  \text{PSF}(\vec r) = 
  \frac{1}{2\pi\sigma^2}
  \left(1-\frac{1}{\gamma}\right)
  \left(1+\frac{u}{\gamma}\right)^{-\gamma},
\end{equation}
where $\sigma$ and $\gamma$ are free parameters
(\cite{matthew_kerr_thesis}).  For radially symmetric extended sources,
the angular part of the integral can be done analytically
\begin{equation}
  \text{PDF}(u)= \int_0^\infty dv
  I_\text{src}(v) 
  \left(\frac{\gamma-1}{\gamma}\right)
  \left( \frac{\gamma}{\gamma + u + v}\right)^\gamma 
  \times ~_2F_1 \left(\gamma/2,\frac{1+\gamma}{2},1,\frac{4uv}{(\gamma+u+v)^2}\right).
\end{equation}
This convolution formula is used by \pointlike because it is faster
and more closely reduces to the PSF when the source's size is 
small.

There will always be a small numerical discrepancy between the PSF and
a very small extended source due to numerical error in the convolution.
In most situations, this error would be insignificant. But when testing
a source for extension, this offset can significantly bias the estimate
of the significance of the extension of a source.  To correct for this,
when testing a source for extension we compare the likelihood fitting
the source with an extended shape to the likelihood fitting it with its
extension fixed to ${10^{-10}}\deg$.

\subsection{Extension Errors}
\label{extension_error}

Errors on fit parameters are typically calculated in one of two
ways. The first method requires explicitly varying a parameter
while simultaneously optimizing the other parameters
until the log of the likelihood has fallen by a particular value.
The \minuit fitting
package provides the {\em Simplex} function to calculate errors this way
(\cite{minuit_documentation}).  The second method involves estimating the
likelihood function as being a multivariate Gaussian and calculating the
curvature of the log of the likelihood at the peak to estimate when the
function will decrease by the desired value. \minuit provides the {\em HESSE}
algorithm to calculate errors this way.  {\em HESSE} errors 
can be calculated significantly faster.

We found that the {\em HESSE} errors on the extension of a source
were sometimes badly estimated.  On the other hand, the {\em Simplex}
algorithm was prohibitively slow and would often fail to convergence. Our
approach to calculating extension errors is to fix the position of the
source and varying just the extension using the {\em Simplex} algorithm.
This approach makes the approximation that the covariance between each
spatial parameter is small but not that the likelihood is Gaussian. This
method is shown schematically in figure~\ref{four_plots_ic443}(a) which
shows the change in \loglikelihood when varying the extension of the
SNR IC443.  The localization error is separately calculated by fixing
the extension and spectrum of the source and fitting a parabola to the
likelihood as a function of position.

\subsection{\gtlike Crosscheck}
\label{gtlike_crosscheck}

\pointlike is important for LAT analysis that require many iterations
such as source localization and extension fitting.  On the other hand,
because of the fewer approximations used in calculating the likelihood
we expect that the spectral parameters fit by \gtlike to be slightly
more precise.  Furthermore, because \gtlike is the standard likelihood
analysis package, it has been more extensively validated for spectral
analysis.  For that reason, in the following analysis  we use \pointlike
to determinate the position and extension of a source and then determine
the spectrum using \gtlike. Both \gtlike and \pointlike can estimate
the statistical significance of the extension of a source and we require
that both methods agree to claim a detection.

We found good agreement between the two methods. For the new extended
source candidates, table~\ref{alt_diff_model_results} will shows a
comparison of \ts and \tsext computed using \pointlike and \gtlike.
Unless explicitly mentioned, all \ts, \tsext, and spectral parameters
were calculated using \gtlike using \pointlike's positions and extensions.

@@

There is a degeneracy between a spatially extended source and multiple
point sources.  To assess the possibility of source confusion,
we developed a function in \pointlike to simultaneously fit the position
of two point sources.  To improve the robustness of the fit, the sum and
difference of the positions of the two sources are fit in a coordinates
rotated to the equator.  The \loglikelihood is then maximized by fitting
the sum and difference of the positions.

We define \tsinc as twice the increase in \loglikelihood fitting the
region as two point sources compared to fitting the region as one point
source: \begin{equation}
  \tsinc=2\times(\loglikelihood_\text{2pts}-\loglikelihood_\text{ps}).
\end{equation} \tsinc can not be directly compared to \tsext to see
which model is more significant because the models are not nested
(\cite{statistics_with_care}). Even though the comparison of \tsext
with \tsinc is not a calibrated test, we find the extreme cases $\tsinc
\loglikelihood \tsext$ or $\tsinc\gg\tsext$ to be suggestive and we only
consider a source to be extended if $\tsext>\tsinc$.

Like extended sources described in section~\ref{gtlike_crosscheck},
the spectrum of the two point sources can be refit using \gtlike.
we quote the spectral values obtained from \gtlike using the best fit
positions found using \pointlike.  For the extended candidates found
by our search, we computed both \tsext and \tsinc.  The results will be
presented in table~\ref{dual_localization_results}.

@@

The spatial shape of extended sources can be modeled
as a two dimensional Gaussian
\begin{equation}\label{gauss_pdf}
  \text{PDF}(x,y)=\tfrac{1}{2\pi\sigma^2}\exp\left(-(x^2+y^2)/2\sigma^2\right)
\end{equation}
or a uniform disk
\begin{equation}\label{disk_pdf}
  \text{PDF}(x,y)=\tfrac{1}{\pi\sigma^2}\delta\left(x^2+y^2<\sigma^2\right).
\end{equation}
Although these shapes are significantly different, the convolution of them
with the PSF look similar.  Figure~\ref{compare_disk_gauss} demonstrates
this by showing the PSF, PDF, and convolution of the PDF with the PSF
for a uniform disk and Gaussian spatial model of size 0.5\deg.  This plot
shows that we are not very sensitive to probing the exact structure of an
extended source.  In the following we assume a uniform disk spatial model.

To get the convolved shapes to match in figure~\ref{compare_disk_gauss},
we had to set them to predict the same 68\% containment
radius of 0.5\deg.  The 68\% containment radius for a
spatial model is the radius at which 68\% of the intensity is
enclosed.  It can be computed by a straightforward integral
and we find that $\rsixeight_\text{,Gaussian}=1.51\sigma$
whereas $\rsixeight_\text{,disk}=0.82\sigma$ where $\sigma$
is defined in equation~\ref{disk_pdf} for the Gaussian source and
equation~\ref{gauss_pdf} for the disk source.  Since $\rsixeight=0.5\deg$,
the uniform disk has $\sigma=0.41\deg$ and the Gaussian has
$\sigma=0.75\deg$.

This is important when comparing morphologies to other wavelengths
because the quoted size can vary significantly depending on which quantity
is reported.  This effect can be best seen in figure~\ref{compare_r68}
which a counts map of an extended source simulated in the energy
range from 1 \gev to 100 \gev with a uniform disk spatial model with
an extension $\sigma$ of 0.5. Overlaid on the plot is the fit extension
assuming the source has a uniform disk and a Gaussian spatial model. The
plot overlays both $\sigma$ and $\rsixeight$ and $\sigma$ is significantly
larger for the disk spatial hypothesis compared to the Gaussian spatial
model. On the other hand, the disk and Gaussian's 68\% containment radius
are similar.

Since we are not very sensitive to the particular morphology of an
extended source, there is no correct choice for which size to quote
or which shape to overlay. For the following analysis, we quote the
disk's edge and overlay this size.  But due to smearing of the PSF,
$\sigma$ typically looks larger than the observed counts distribution.
When comparing the fit extensions with other wavelengths, it is important
to compare consistent quantities.

\section{LAT Extended Source Validation}

@@

We validated \pointlike's extension fitting code with a Monte Carlo
study. \tsext (defined in section~\ref{extension_fitting}) can be used to calculate the statistical significance
of the extension of a source.  Since the point source and extended source models are
nested, an extended source must always fit as well as a point source.  On the other hand, we would
not expect the likelihood to change very much unless the source was
significantly extended.  Since an extended source has one additional
degree of freedom, Wilks' Theorem predicts that the distribution of $\tsext$
when testing a point source for extension should follow a $\chi^2_1$
distribution (\cite{wilks_theorem}).

However, since the null hypothesis rests on the edge of
parameter space when the extension is 0, Wilks' Theorem does not hold
(\cite{warn_wilks_theorem}).  One might expect the actual distribution
to be a half $\chi^2_1$ distribution with one degree of freedom plus
half a delta function at 0:
\begin{equation}
  P(\ts)=\tfrac{1}{2}(\chi^2_1(\ts)+\delta(\ts)).
\end{equation}
Chernoff proved that under certain assumptions this is the correct distribution
when the null hypothesis is on the edge of parameter
space (\cite{chernoff}).  The false detection
probability can be estimated by integrating this function from an observed
test statistic value to infinity. It is for this particular distribution
that the often quoted result holds that $\sqrt{\ts}$ is a measure of
the number of $\sigma$ of the detection (\cite{mattox_egret}).

The half $\chi^2_1$ distribution was found to hold for the special case
of source finding using EGRET (\cite{mattox_egret}). This distribution
is also plausible when testing point sources for extension. Due to
statistical fluctuations, half of the point sources might look narrower
than the PSF leading to $\tsext=0$. The other half of the time, we would
get a distribution consistent with Wilks' theorem. We will present a
Monte Carlo study that shows an empirical distribution of \tsext in the
null hypothesis and compares it to this distribution.

We simulated point sources of varying spectral models and fit them
them using \pointlike as both point and extended sources. The data was
simulated using \gtobssim\footnote{\gtobssim is distributed
by the Fermi Science Support Center (\cite{fssc}).}
The point sources were simulated with a power-law spectral model with
six $>100$ \mev fluxes ranging from $3\times 10^{-9} \ph/\cm^2/\sec$ to
$10^{-6} \ph/\cm^2/\sec$.  The point sources were simulated with spectral
indices ($\gamma$) of 1.5, 2, 2.5, and 3.  These values were picked to
to represent typical source parameters in LAT-detected sources. The point
sources were simulated on top of an isotropic power-law background
with a Sreekumar-like spectrum ($>100$ \mev flux of $1.5\times 10^{-5}$ and spectral
index 2.1) (\cite{sreekumar_isotropic}).  The Monte Carlo simulation was
performed over a one year time interval using a default rocking profile
and a representative livetime fraction of 0.8.  The reconstruction was
performed with photons from an energy range of 1 \gev to 100 \gev using 4
energy bins per decade and using the 
Pass 7\_V6 (P7\_V6) Source Instrument
Response Function (IRFs).  For each point source, we used \pointlike
to fit it as both a point and extended source and calculate \tsext and
we only kept the sources which had a significant point source detection
($\ts>25$).

For most of the spectral models, ~30,000 statistically independent
simulations were performed. For the dimmer spectral models, many of the
simulations had $\ts<25$ and were discarded.  Table~\ref{ts_ext_num_sims}
shows the different spectral models used in our study as well as the
number of simulations.  The cumulative density of \tsext is plotted in
figure~\ref{ts_ext_mc}. The $\chi^2_1/2$ distribution suggested by Wilks'
Theorem is overlaid for comparison.

Our Monte Carlo study shows broad agreement between simulations and Wilks'
theorem. Nevertheless, the agreement is not perfect.  It should be noted
that the discrepancy seems to be worst for bright sources which seems to
imply that numerical errors in the convolution become more apparent for
sufficiently bright sources.  Other possible reasons for departure from
Wilks' theorem might include \pointlike ignoring energy dispersion which
would change the PSF's shape as a function of energy. But we emphasize
that most of the time, our empirical curve lies to the left of the
theoretical curve so using the theoretical distribution would lead to an
underestimate of the statistical significance of a detection. Therefore,
we are confident that $\sqrt{\tsext}$ can be used as a measure of the
statistical significance of a source's extension and use it in the
following analysis.

@@

We calculated the LAT's detection threshold to spatially
extended sources. The detection threshold to extension is
defined as the flux at which the average value of $\tsext$ is
$\langle\tsext\rangle=16$ corresponding to a $4\sigma$ detection (see
section~\ref{monte_carlo_validation}).  Qualitatively, we expect the LAT
would not be sensitive to sources much smaller than the PSF or much larger
than the PSF.  Small sources would look too much like the PSF and larger
sources would get lost in the background due to low surface brightness.

To calculate the LAT's detection threshold, we simulated sources with
a uniform radially symmetric disk spatial model on top of a power-law
Sreekumar-like isotropic spectrum (\cite{sreekumar_isotropic}).  The Monte
Carlo simulation was performed using the same two year time range that
was used in 2FGL.  For each extension and spectral index, we picked a
flux range which bracketed $\tsext=16$. We then picked ten flux points in
this range and repeatedly simulated and then performed extension tests of
the simulated extended source.  We calculated $\langle\tsext\rangle=16$
by fitting a line to the flux and $\tsext$ values.

@@

Of the 815 clean AGN, we select 775 of these 2FGL sources which
are significant above 1 \gev and fit each of them for extension.
A histogram of the \tsext values computed for these AGN is shown in
figure~\ref{agn_ts_ext}. Overlaid on the plot is a $\chi^2/2$ distribution
suggested by Wilks' Theorem.  The \tsext distribution for AGN shows good
agreement with the theoretical distribution.  Two sources had $\tsext>9$.
One was due to incorrectly pruning a nearby catalog sources and the
other was due to a failure of convergence of the point hypothesis.
This result demonstrates that we can use \tsext as a measure of the
statistical significance of the detection of the extension of a source.

@@

Note about this this paper finds other stuff: (\cite{discovery_of_pwn_for_PSR_J1617-5055}).

The \gev emission is suggested to be the same emission component as
the \tev emission, but further observations of this source at other
frequencies will likely be needed to firmly associated this source.

@@

This source is spatially coincident with the extended
\tev source HESS\,J1614-518 (\cite{hess_plane_survey}). In
figure~\ref{1FGL_J1613.6-5100c}, contours of HESS\,J1614-518 are overlaid
on 2FGL\,J1615.2-5138.  The H.E.S.S. experiment measured a Gaussian
extension of $\sigma=0.23\deg\pm0.02\deg$ and $\sigma=0.15\pm0.02$ in
the semi-major and semi-minor axis. This size corresponds to a 68\%
containment size of $\rsixeight=0.35\deg\pm0.03\deg$ and $0.23\pm0.03$.
This elliptical size matches the LAT size $\rsixeight=0.35\deg\pm0.03\deg$.
Figure~\ref{hess_seds} shows that the LAT spectrum of 2FGL\,J1615.2-5138
connects smoothly to the H.E.S.S spectrum of HESS\,J1614-518.

\todo[inline]{Add interpretations of HESS\,J1614-518. Stefan says to
use the Rowell et al, Suzaku observations.}

@@

The increased \gev and \tev size compared to the X-ray size
has previously been observed in several aging PWNe including 
HESS\,J1825-137 (\cite{hess_j1825_xmm_newton,hess_j1825_hess} and HESS\,J1640-465
(\cite{hess_plane_survey,xmm_newton_hess_j_1640-466}) and can be explained
by the electrons emitting syncrotron radiation having a shorter lifetime
than the electrons emitting inverse Compton radiation.

Because of the spectral and spatial match between the \gev and \tev
emission, the LAT data naturally fits into this model as being the rising
edge of the inverse Compton component of a PWN.

@@

\section{Conclusion}

\todo[inline]{This conclusion needs to be written.}

Many extended sources. Instructive to use photons with energy
above 10 \gev where we don't have to worry about diffuse background
as much.

Make some conclusion about how the LAT will eventually collect a factor
of five more data! \pointlike will be necessary to improve the model of
the high energy sky. Hard to do a blind analysis of LAT data.

Figure~\ref{allsky_extended_sources} is an all sky map showing the
location of all \gev extended sources. Note how most extended sources
are in the Galactic plane.

Figure~\ref{gev_vs_tev_histogram} is a histogram comparing the size of
all extended sources seen in \gev by the LAT and in \tev by H.E.S.S..
Note how H.E.S.S. can see smaller sources whereas the LAT can see
bigger sources.

For all extended sources seen both in \gev and \tev,
figure~\ref{gev_vs_tev_plot} shows a comparison of their sizes.
Note that there is pretty good agreement.

Note about how comparison of HESS and LAT sizes will require more accurate
ellitpical gaussian fitting + using the same spatial model.  Interesting
to see if there is a correlation for PWN between energy and source size!

LAT has a planned lifetime of 5 years with (don't know how to phrase this) 
hope to run for 10 years. Additonal data will allow us to perfrom
more detailed morphological and spectral analysis of these sources.

Improved diffuse model and better statisticsl will allow us to push
our analysis to lower energies.

>>>>

In \pointlike, it is assumed that the spatial and spectral
model of an extended source are separable, i.e. that the source
model $M(l,b,E)=S(l,b)\times X(E)$.  To fit an extended source,
\pointlike convolves the extended source shape with the PSF (as a
function of energy) and uses the \minuit library to maximize the
likelihood by simultaneously varying the position and extension of
the source (\cite{minuit_documentation}).  As will be described in
section~\ref{monte_carlo_validation}, simultaneously fitting the position
and extension is necessary to correctly calculate the statistical
significance of the detection of extension.  For each position and
extension, the spectral parameters of the sky model are refit.  To avoid
projection effects, the fitted source position parameters are not the
source's longitude and latitude but instead the source's displacement
in a rotated reference frame.

The significance of the extension of a source can be calculated
from \tsext, which 
is the test statistic of the likelihood ratio test of
a model with a spatially extended source and a model
with a point-like source and defined as
\begin{equation}
  \tsext=2\log(\loglikelihood_\text{ext}/\loglikelihood_\text{ps}).
\end{equation}
where \loglikelihood is the log of the Poisson likelihood.
\pointlike calculates \tsext by fitting a source first with a spatially
extended model and then as a point source.  The interpretation
of \tsext in terms of a statistical significance is discussed in
section~\ref{monte_carlo_validation}.

For extended sources with an assumed radially symmetric shape,
we use a semi-analytic calculation to speed up the calculation of
the expected photon distribution. The expected photon 
distribution can be written as
\begin{equation}
  \text{PDF}(\vec r) = \int  \text{PSF}(|\vec r - \vec r'|)I_\text{src}(\vec r') d A'.
\end{equation}
For the LAT, the PSF can be parameterized by a {\em King function}
\begin{equation}
  \text{PSF}(\vec r) = 
  \frac{1}{2\pi\sigma^2}
  \left(1-\frac{1}{\gamma}\right)
  \left(1+\frac{u}{\gamma}\right)^{-\gamma},
\end{equation}
where $\sigma$ and $\gamma$ are free parameters
(\cite{matthew_kerr_thesis}).  For radially symmetric extended sources,
the angular part of the integral can be done analytically
\begin{align}
  \text{PDF}(u) & = \int_0^\infty \sigma^2 dv 
  I_\text{src}(v) 
  \int_0^{2\pi} d\phi' 
  \text{PSF}(\sqrt{2\sigma^2(u+v-2\sqrt{uv}\cos(\phi-\phi'))})
  \\
  & = \int_0^\infty dv
  I_\text{src}(v) 
  \left(\frac{\gamma-1}{\gamma}\right)
  \left( \frac{\gamma}{\gamma + u + v}\right)^\gamma 
  \times {}_2F_1 \left(\gamma/2,\frac{1+\gamma}{2},1,\frac{4uv}{(\gamma+u+v)^2}\right).
\end{align}
where $u=(r/\sigma)^2/2$, $v=(r'/\sigma)^2/2$, and ${}_2F_1$ is the
Gaussian hypergeometric function.  This convolution formula is used by
\pointlike, reducing the calculation of the expected photon distribution
to a single numerical integral.

There will always be a small numerical discrepancy between the expected
photon distribution derived from a true point source and a very small
extended source due to numerical error in the convolution.  In most
situations, this error would be insignificant.  But in particular for
very bright sources, this numerical error has the potential to bias the
test statistic for the extension test.  the source with an extended shape
to the likelihood fitting it with its extension fixed to ${10^{-10}}\deg$.

We estimate the errors on the extension
by recalculating the likelihood for a set of extension values
while keeping the position fixed.

We estimate the error on the extension of a source by fixing the position
of the source and varying the extension until the likelihood has fallen
by $\tfrac{1}{2}$, corresponding to a $1\sigma$ error.  This method is
shown schematically in figure~\ref{four_plots_ic443}(a) which shows the
change in \loglikelihood when varying the extension of the SNR IC443.
The localization error is calculated by fixing the extension and spectrum
of the source and fitting a Gaussian to the likelihood as a function
of position.

\subsection{\gtlike Analysis Validation}
\label{gtlike_crosscheck}

\pointlike is important for LAT analysis that require many iterations
such as source localization and extension fitting.  On the other hand,
because of the fewer approximations used in calculating the likelihood
we expect the spectral parameters found with \gtlike to be slightly
more precise.  Furthermore, because \gtlike is the standard likelihood
analysis package, it has been more extensively validated for spectral
analysis.  For that reason, in the following analysis  we use \pointlike
to determinate the position and extension of a source and then determine
the spectrum using \gtlike. Both \gtlike and \pointlike can be 
used to estimate
the statistical significance of the extension of a source and we require
that both methods agree to claim a detection.

We found good agreement between the two methods. For the new extended
source candidates, table~\ref{alt_diff_model_results} will shows a
comparison of the test statistic \ts and \tsext computed using \pointlike
and \gtlike.  Unless explicitly mentioned, all \ts, \tsext, and spectral
parameters were calculated using \gtlike using \pointlike's positions
and extensions.

@@

There is a degeneracy between a spatially extended source and multiple
point sources that are separated by angular distances comparable or
smaller than the size of the LAT PSF.  To assess the possibility of source
confusion, we developed a function in \pointlike to simultaneously fit
the position of two point sources.

We define \tsinc as twice the increase in \loglikelihood fitting the
region as two point sources compared to fitting the region as one point
source: 
\begin{equation}
  \tsinc=2\times(\loglikelihood_\text{2pts}-\loglikelihood_\text{ps}).
\end{equation} 
\tsinc can not be directly compared to \tsext to see which
model is more significant because the models are not nested
(\cite{statistics_with_care}). Even though the comparison of \tsext with
\tsinc is not a calibrated test, we find the cases $\tsinc \ll \tsext$
or $\tsinc\gg\tsext$ suggestive and we only consider a source to be
extended if $\tsext>\tsinc$.

Like extended sources described in section~\ref{gtlike_crosscheck},
the spectrum of the two point sources can be refit using \gtlike.
We quote the spectral values obtained from \gtlike using the best fit
positions found using \pointlike.  For the extended candidates found
by our search, we computed both \tsext and \tsinc.  The results will be
presented in table~\ref{dual_localization_results}.

@@

We tested two different models for the
spatial shape, either a two dimensional Gaussian
\begin{equation}\label{gauss_pdf}
  I(x,y)=\tfrac{1}{2\pi\sigma^2}\exp\left(-(x^2+y^2)/2\sigma^2\right)
\end{equation}
or a uniform disk
\begin{equation}\label{disk_pdf}
  I(x,y)=
  \begin{cases}
    \frac{1}{\pi\sigma^2} & x^2+y^2\le\sigma^2 \\
    0                      & x^2+y^2>\sigma^2
  \end{cases}
\end{equation}
Although these shapes are significantly different, the convolution
of them with the PSF look similar.  Figure~\ref{compare_disk_gauss}
demonstrates this by showing $I_\text{src}$, the PSF, and the PDF for
a uniform disk and Gaussian spatial model of size 0.5\deg.\footnote{To
allow a valid comparison between Gaussian and disk shaped morphologies,
we define the source size for this test as the radius containing
68\% of the intensity ($\rsixeight$).  $\rsixeight_\text{,Gaussian}=1.51\sigma$
and $\rsixeight_\text{,disk}=0.82\sigma$ where $\sigma$
is defined in equation~\ref{gauss_pdf} and
equation~\ref{disk_pdf} respectively.} This plot shows that we are
not very sensitive to probing the exact structure of an extended source.
In the search for extended sources, we therefore use only a uniform
disk as our spatial extension shape. We then quote the radius of the
disk edge as the size of the source.

\section{Validation of Analysis Method}

@@

Mattox et al. discuss that the test statistic distribution
for a likelihood ratio test on the existence of a source at
a given position is \cite{mattox_egret}
\begin{equation}\label{ts_ext_distribution}
  P(\ts)=\tfrac{1}{2}(\chi^2_1(\ts)+\delta(\ts)).
\end{equation}
The particular form of equation \ref{ts_ext_distribution} is
due to the null hypothesis (source flux $\Phi=0$) residing
on the edge of parameter space and the model hypothesis
adding a single degree of freedom. It is plausible to
expect a similar distribution of the test statistic
in the test for source extension as the same conditions
apply (with source flux $\Phi$ replaced by source radius $r$).
To validate this claim, we performed a Monte Carlo
study to calculate empirical distributions for $\tsext$ and
compared them to equation~\ref{ts_ext_distribution}.

We simulated point sources of varying spectral models using
\gtobssim\footnote{\gtobssim is distributed
by the Fermi Science Support Center (\cite{fssc}).}
and fit them
them using \pointlike as both point and extended sources. 
The point sources were simulated with a power-law spectral model 
with integrated fluxes above 100 \mev ranging from
$3\times 10^{-9}$ to $10^{-6} \ph/\cm^2/\sec$ in
six discrete steps and spectral
indices ranging from 1.5 to 3 in four discrete steps.
These values were picked to
to represent typical source parameters in LAT-detected sources. The point
sources were simulated on top of an isotropic 
background with an integrated flux above 100 \mev of $1.5\times10^{-5}$
(\cite{sreekumar_isotropic}).  The Monte Carlo simulation was
performed over a one year observation period
using a default rocking profile
and a representative livetime fraction of 0.8.  The reconstruction was
performed using 1-100 \gev photons 
and the 
Pass 7\_V6 (P7\_V6) Source Instrument
Response Function (IRFs).  For each point source, we used \pointlike
to fit it as both a point and extended source and calculate \tsext and
we only kept the sources which had a significant point source detection
($\ts>25$).

For most of the spectral models, ~30,000 statistically independent
simulations were performed. For the dimmer spectral models, many of the
simulations left the source undetected ($\ts<25$)
and were discarded.  Table~\ref{ts_ext_num_sims}
shows the different spectral models used in our study as well as the
number of simulations.  The cumulative density of \tsext is plotted in
figure~\ref{ts_ext_mc}. The $\chi^2_1/2$ distribution of
equation~\ref{ts_ext_distribution} is overlaid for comparison.

Our Monte Carlo study shows broad agreement between simulations and
equation~\ref{ts_ext_distribution}. Nevertheless, the agreement is not
perfect.  It should be noted that the discrepancy seems to be worst for
bright sources, a likely cause being numerical errors in the convolution
becoming more apparent for sufficiently bright sources.  Other possible
reasons for departure from equation~\ref{ts_ext_distribution} could
be that \pointlike ignores energy dispersion which would change the
PSF's shape as a function of energy. We emphasize that most of the
time, our empirical curve lies to the left of the theoretical curve so
using the theoretical distribution would lead to an underestimate of the
statistical significance of a detection. Therefore, we are confident that
$\sqrt{\tsext}$ can be used as a conservative measure of the statistical
significance of a source's extension and use it in the following analysis.

@@

We calculated the LAT's detection threshold to spatially extended
sources. We define the detection threshold as the flux at which the value
of $\tsext$ averaged over many statistical representations of a source
is $\langle\tsext\rangle=16$ corresponding to a $4\sigma$ detection
(see section~\ref{monte_carlo_validation}).

We used the simulation setup described in
section~\ref{monte_carlo_validation}, but instead simulated extended
sources with a uniform radially symmetric disk spatial model and
instead over the actual two year time interval.  For each extension and
spectral index, we picked a flux range which bracketed $\tsext=16$. We
then picked ten flux points in this range and repeatedly simulated
and then performed extension tests of the simulated extended source.
We calculated $\langle\tsext\rangle=16$ by fitting a line to the flux
and $\tsext$ values.

@@

Of the 815 clean AGN, we select 775 of these 2FGL sources which
are significant above 1 \gev and fit each of them for extension.
A histogram of the \tsext values computed for these AGN is shown in
figure~\ref{agn_ts_ext}. Overlaid on the plot is the $\chi^2/2$
distribution of equation~\ref{ts_ext_distribution}.
The \tsext distribution for AGN shows good
agreement with the theoretical distribution.  Two sources had $\tsext>9$.
One was due to incorrectly pruning a nearby catalog sources and the
other was due to a failure of convergence of the point hypothesis.
This result demonstrates that we can use \tsext as a measure of the
statistical significance of the detection of the extension of a source.

@@

\todo[inline]{
Note about how it is difficult to explain the TeV to X-ray emission
ratio b/c of magnetic field. Refernece in page 7 of (sukazu paper on HESS J1614-518, but
it also refers to (Matsumoto et. al 2007 and says this requires small b/field with strong
cutoff in eletron energy). Also some not eabout different photon fields
being possible.}

\todo[inline]{
Note about this this paper finds other stuff: (\cite{discovery_of_pwn_for_PSR_J1617-5055}).
}

\todo[inline]{
The \gev emission is suggested to be the same emission component as
the \tev emission, but further observations of this source at other
frequencies will likely be needed to firmly associated this source.
}

@@

This source is spatially coincident with the extended
\tev source HESS\,J1614-518 (\cite{hess_plane_survey}). In
figure~\ref{1FGL_J1613.6-5100c}, contours of HESS\,J1614-518 are overlaid
on 2FGL\,J1615.2-5138.  The H.E.S.S. experiment measured a Gaussian
extension of $\sigma=0.23\deg\pm0.02\deg$ and $\sigma=0.15\pm0.02$
in the semi-major and semi-minor axis. This size corresponds
to a 68\% containment size of $\rsixeight=0.35\deg\pm0.03\deg$
and $0.23\pm0.03$.  This elliptical size matches the LAT size
$\rsixeight=0.35\deg\pm0.03\deg$.  Figure~\ref{hess_seds} shows that
the LAT spectrum of 2FGL\,J1615.2-5138 connects smoothly to the H.E.S.S
spectrum of HESS\,J1614-518.  Further data collected by H.E.S.S. in 2007
helped to resolve a double peaked structure in the H.E.S.S. data but no
spectral variation across the source, suggesting that the emission is
not the confusion of physically separate sources (\cite{closer_look_hess_j1614-518}).
The source was also detected by CANGAROO-III (\cite{cangaroo_j1614-518}).

This source is currently unidentifed. There are five nearby pulsars,
but they are not luminous enough to provide the required energy output
to power the \tev emission (\cite{closer_look_hess_j1614-518}).

\todo[inline]{Swift observations}

Suzaku observations of the region around HESS\,J1614-518 reveale three
X-ray sources in the region. Suzaku source A is a hard extended source
spatially coincident with the peak of HESS\,J1614-518.

Suzaku source B is
in a relativly dim region in the middle of HESS\,J1614-518 and was not
spatially resolvable. source B is spatially coincident with Pisim 22.

Suzaku Source C is a foreground source.

Swift observations the region and resolved six X-ray sources.\todo{citation}

\todo[inline]{Emission due to SNR}

\todo[inline]{Emission could be due to a PWN}

\todo[inline]{Emission due to Massive Star}

\todo[inline]{Add interpretations of HESS\,J1614-518. Stefan says to
Suzaku observations.}

@@

The increased \gev and \tev size compared to the X-ray size
has previously been observed in several aging PWNe including 
HESS\,J1825-137 (\cite{hess_j1825_xmm_newton,hess_j1825_hess}, HESS\,J1640-465
(\cite{hess_plane_survey,xmm_newton_hess_j_1640-466}),
and Vela X (\cite{vela_x_rosat,vela_x_hess}). 
This can be explained by a different synchrotron cooling
time for the electroncs producing X-rays and \tev gamma rays.
Because of the spectral and spatial match between the \gev and \tev
emission, the LAT data naturally fits into this model as being the rising
edge of the inverse Compton component of a PWN.

@@

\section{Discussion}

\todo[inline]{Finish the discussion.}

2FGL reported on the detection of twelve spatially extended sources. Using
two years of LAT data and a new analysis method, we present on 
the detection of nine additional extended sources. We also reanalyze
the spatial shape of the extended sources in 2FGL.  Finding a coherent
source extension with different frequencies, especially at \tev energies,
allows us to identify the LAT source. Even still, for many extended LAT
sources the source class and emission process is still uncertain.

The position of the 21 extended LAT sources is plotted in
figure~\ref{allsky_extended_sources}.  Most of them lie along the galactic
plane.  This is expected because extragalactic sources are typically too
far away to be resolvable and most Galactic sources lie along the plane.

Figure~\ref{compare_index_2FGL} shows a comparison of the spectral index
of LAT detected extended sources and of all sources in 2FGL. This, and
table~\label{known_extended_sources} and~\label{new_ext_srcs_table},
show that the LAT observes a population of hard (index $<2$)
extended sources above 10 \gev which connects to \tev sources.
Figure~\ref{hess_seds} shows the LAT energy spectrum of four of the
extended sources which were first discovered in the H.E.S.S. Galactic
plane survey (\cite{hess_plane_survey}) and have a matching size to LAT
extended sources.  The LAT energy spectrum connects smoothly to \tev.
This is also true of HESS\,J1825-137 (\ref{fermi_hess_j1825}) and RX
J1713.7-3946 (\cite{rx_j1713_lat}). We conclude that the \gev and \tev
emission from these sources is coming from the same emission mechanism.

For the LAT extended sources also seen in \tev,
figure~\ref{gev_vs_tev_plot} shows a comparison of their sizes.  There is
a good correlation between the \gev and \tev sizes of the sources. Even
so, the size of PWNe are expected to vary across the \gev and \tev energy
range and the size of HESS\,J1825-137 was seen by H.E.S.S. to vary
between 200 \gev and 20 \tev (\cite{energy_dependent_hess_j1825}).
HESS\,J1825-137 is significantly larger in \gev than \tev
(\cite{fermi_hess_j1825}).  It is interesting to compare the \gev and
\tev size of other PWN candidates, but definitively measuring this effect
would require a more careful analysis of the LAT data using the same 
elliptical spatial model.

Figure~\ref{gev_vs_tev_histogram} compares the size of the 21 extended
LAT sources to the 42 extended H.E.S.S. sources.  Because of the large
field of view and all sky coverage, the LAT can more easily measure
larger sources including the LMC and SMC.  On the other hand, the
smaller angular resolution of Air Cherenkov detectors allows them to
measure a population of extended sources below our sensitivity limit
(currently at about $\approx0.2\deg$).  Fermi has a five year nominal
livetime with a goal of ten years of operation. With increased exposure,
the LAT will likely begin to resolving these smaller \tev sources.
